Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-01-18 SupportingInformation.Rmd
minor edit

```{r cause4copula_stat_ar1_clayton, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model 
resloc<-"./Results/Cause4copula_results/"
model<-"ar1"
params<-c(0.5) # this parameter is beta in ar1 model
fcode<-3

@@

params<-c(-0.5) # this parameter is beta in ar1 model
tempo<-paste(resloc,"Cause4copula_stat_results_",model,"_beta_",params,"_",BiCopName(fcode,short=F),sep="")

@@

```{r cause4copula_stat_ar1_survivalclayton, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model 
resloc<-"./Results/Cause4copula_results/"
model<-"ar1"
params<-c(0.5) # this parameter is beta in ar1 model
fcode<-13

@@

params<-c(-0.5) # this parameter is beta in ar1 model
tempo<-paste(resloc,"Cause4copula_stat_results_",model,"_beta_",params,"_",BiCopName(fcode,short=F),sep="")

>>>>

```{r cause4copula_stat_ar1_clayton, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : clayton

model<-"ar1"
fcode<-3

# for positive beta
params<-c(0.5) # this parameter is beta in ar1 model
resloc<-"./Results/Cause4copula_results/"

@@

# for negative beta
resloc<-"./Results/Cause4copula_results/"
params<-c(-0.5) # this parameter is beta in ar1 model
tempo<-paste(resloc,"Cause4copula_stat_results_",model,"_beta_",params,"_",BiCopName(fcode,short=F),sep="")

@@

```{r cause4copula_stat_ar1_survivalclayton, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : survival clayton
model<-"ar1"
fcode<-13

# for positive beta
params<-c(0.5) # this parameter is beta in ar1 model

resloc<-"./Results/Cause4copula_results/"
tempo<-paste(resloc,"Cause4copula_stat_results_",model,"_beta_",params,"_",BiCopName(fcode,short=F),sep="")

@@

# for negative beta
params<-c(-0.5) # this parameter is beta in ar1 model

resloc<-"./Results/Cause4copula_results/"
tempo<-paste(resloc,"Cause4copula_stat_results_",model,"_beta_",params,"_",BiCopName(fcode,short=F),sep="")
